# This is prep_ohibc.Rmd

This script creates the British Columbia webapp. 

Each R chunk below will not be evaluated (ie, `{r, eval=F}`). 

## 1. setup
```{r setup, eval=F}

# libraries
library(tidyverse)
library(stringr)
library(rgdal)

dir_custom = '~/github/ohi-webapps/custom/northeast'


# create directories on git-annex
dir.create(file.path(dir_annex, key))
dir.create(file.path(dir_annex, key, 'spatial'))
dir.create(file.path(dir_annex, key, 'layers'))

```


## 2. copy map from @jafflerbach's shape files  

Read in BC shapefile and begin formatting for OHI.
I also copied the Canada national flag for British Columbia.


```{r copy bc map from shapefile, eval=F}

# read in shp files and save with desired headers in data frame. ohibc_rgn_wgs84 is in the correct projection for webapps
shp = readOGR(dsn = path.expand('~/github/ohi-northeast/spatial'),
              layer = 'ne_ohi_rgns')

## plot 
# plot(shp)

# view data
shp_data = shp@data; shp_data

# # clean orphan holes or invalid geometries 
# source('~/github/ohi-webapps/custom/cleangeo_spatial_fxn.r')
# bc_clean = cleangeo_spatial(ne)


# save as shapefiles. will create 4 files: .dbf, .prj, .shp, .shx
writeOGR(shp, dsn = file.path(dir_annex, 'northeast/spatial/custom'), 
         layer = 'northeast_shp', driver = 'ESRI Shapefile', overwrite=T) 

# save lookup table with unique rgn_ids
shp_data %>%
  select(rgn_name, rgn_id) %>%
  arrange(rgn_id) %>%
  write_csv(file.path(dir_custom, 'ohibc_rgns_lookup.csv'))

# save rgn_offshore_data.csv
shp_data %>%
  select(rgn_id, rgn_name, area_km2) %>%
  arrange(rgn_id) %>%
  write_csv(file.path(dir_custom, 'rgn_offshore_data.csv'))

```


## 3. populate key directory in git-annex
Copy files required for populate_draft_branch() into `git-annex/clip-n-ship`. These are storage directories.

```{r}
# copy rgn_offshore_data.csv
file.copy(file.path(dir_custom, 
                    'rgn_offshore_data.csv'),
          file.path(dir_annex, key, 'spatial/rgn_offshore_data.csv'), overwrite=T)

# make TEMPLATE mar_coastalpopn_inland25km_lyr.csv
read.csv(file.path(dir_annex, 
                   'can/layers/mar_coastalpopn_inland25km_lyr.csv')) %>%
  filter(rgn_id <= length(unique(shp_data$rgn_id))) %>%
  write.csv(file.path(dir_annex, key, 'layers/mar_coastalpopn_inland25km_lyr.csv'), row.names=F)
    
```

